A SIMPLE AND EFFICIENT ALGORITHM FOR COMPUTING APPROXIMATE NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION

### 2015-09-26 paper.tex
multiple issues and fixups thereof

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for
  computing approximate Nash-equilibria in two-person zero-sum
  sequential games with  incomplete information and perfect recall
  (like Texas Hold'em poker). Our algorithm only performs basic
  iterations (i.e matvec multiplications, clipping, etc., and no calls
  to external first-order oracles, no matrix inversions, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with incomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with convex polytopial profiles. We prove that
  the number of iterations needed to produce a Nash-equilibrium with a
  given precision is inversely proportional to the
  precision. We also present experimental results on simulated and
  real games (Kuhn poker).
\end{abstract}

@@

\subsection{Notation and terminology}
Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
of all subsets of $X$, or equivalently the set of all binary
functions on $X$. Let $m$ and $n$ be positive integers. Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

@@

The interested reader should refer to \cite{combettes2011proximal} and
the references therein, for a more elaborate exposition on
proximal calculus and its use in modern convex-optimization.

@@

In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used
to solve the equilibrium problem \eqref{eq:gilpin}.
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop.
\cite{gilpinfirst} proposed a modified version of the techniques in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle. Here
$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
\textit{condition number} for the game. The crux of their technique was to
observe that \eqref{eq:gilpin} can further be written a the minimization of
the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:dgap})
for the game\footnote{The minimizers of $G$ are precisely the
  equilibria of the game.}, viz
\begin{eqnarray}
\mathrm{minimize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
\end{eqnarray}
and then show there exists a scalar
$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
\begin{eqnarray}
\text{``distance between }(x, y)\text{ and the set of
equilibria'' } \le G(x, y)/\delta.
\end{eqnarray}
Their
algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
with a geometrically decreasing sequence of tolerance levels
$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
should be noted however that
\begin{itemize}
\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate can
be arbitrarily large for ill-conditioned games.
\item[--] The reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. Most
  notably, the complicated projections $\proj_{Q_k}$ are applied at
  each iteration.%%  Of
  %% course, the existence of a linear algorithm for solving
  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  %% conditions are absent.

@@

\section{Methods}
\label{sec:gsp}
\subsection{The Generalized Saddle-point Problem (GSP) connection}
In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
and \eqref{eq:dual_pb} can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}. The crux of idea
is to remove the linear constraints in the definitions of the strategy
polytopes $Q_k$, by modifying the payoff matrix to yield an equivalent
saddle-point problem.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\subsection{A more comfortable notion of approximate Nash-equilibrium}
\begin{definition}
  Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
  \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged
  subdifferential (or
  $\epsilon$-subdifferential, for short) of $f$ is the set-valued
  function defined by
  \begin{eqnarray}
\partial_\epsilon f(x):= \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}
\end{definition}
The idea behind $\epsilon$-subdifferentials is the following. Say we wish
to minimize the function $f$. Replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
small vector $v$''. In fact, it is easy to see that, for each
point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.

@@

\subsection{Practical considerations}
\paragraph*{\textbf{\textit(a) Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo}, most of the time is spent
pre-multiplying vectors by $A$ and $A^T$ (precisely 3 such operations
are done per iteration). For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagonal structure (each block is itself the
Kronecker product of smaller matrices) which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.%%  For the purpose of
%% completness, we explain the details of the tricks used in
%% \cite{hoda2010smoothing} for speeding up the computation of these
%% matvec products.

@@

\paragraph*{\textit(b) Computing $\|K\|$.}
Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
computed using the power iteration (Perron-Frobenius).

\section{Experimental results}
\label{sec:results}
To assess the practical quality of the proposed algorithm, we
tested it on simulated and real games.
\paragraph*{Experiments on sequential games with incomplete
  information: Kuhn 3-card
  poker.} This game is a simplified form of poker
developed by Harold W. Kuhn. It is a two-person zero-sum game which is
simple enough to serve as a proof-of-concept example but contains all
the complexity traits of a incomplete information sequential game. The
deck includes only three playing cards: a King, Queen, and
Jack. One card is dealt to each player, then the first player must bet
or pass, then the second player may bet or pass. If any player chooses
to bet the opposing player must bet as well ("call") in order to stay
in the round. After both players pass or bet the player with the
highest card wins the pot.%%  The
%% sequence-form representation of the game has $n_1 = n_2 = 13$
%% sequences and $l_1 = l_2 = 7$ information
%% sets per player. The sequence-form of the game is given by\\\\
%% $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
%% E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
%% E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
%% E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
%% E_1(5,5) = E_1(6,9) = {-1}$; $E_2 \in \mathbb{R}^{7 \times 13}$ with
%% $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
%% E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
%% E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
%% E_2(5,0) = E_2(6,0) = {-1}$; and $A \in \mathbb{R}^{13 \times
%%   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
%% {-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
%% A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
%% A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
%% $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
%% A(12,1) = A(12,5) = {0.166667}$.\\

@@

\begin{figure}[!htpb]
  \subfigure[$10^3 \times 10^3$ matrix game on simplexes]{
    \includegraphics[width=.5\linewidth]{0.pdf}
  }
  %% \hspace{-2em}
  %% \subfigure[Toy poker]{
  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
  %% }
  \hspace{-2em}
  \subfigure[Kuhn 3-card poker]{
    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-.5em}
  \includegraphics[width=.5\linewidth]{1.pdf}
  %% \hspace{-1em}
  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  %\hspace{.5em}
  \includegraphics[width=.49\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. In \textit{(a)}, the duality gaps
    are computed according to formula \eqref{eq:mg_pd}. One can see
    the linear (i.e exponential) behavior of the algorithm in
    \cite{gilpinfirst}, inbetween consecutive breakpoints on the
    $\epsilon$ grid (though the rate of exponential growth seems to by
    quite close to $1$ here). The first-order smoothing algorithm from
    \cite{nesterov2005a} jitters around as the iterations go on
    because even the smoothed problem becomes heavily ill-conditioned
    near solutions. On the other hand, our proposed
    algorithm beats both of the aforementioned algorithms, and
  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
  verified empirically.}
  \label{Tab:dgap_curve}
\end{figure}

\section{Concluding remarks and future work}
Making use of the sequence-form representation
\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
devised a simple and efficient primal-dual algorithm for computing
Nash-equilibria in two-person zero-sum sequential games with
incomplete information (like Texas Hold'em, etc.). Our algorithm is
simple to implement, with a low constant cost per iteration, and
enjoys a rigorous convergence theory with a proven
$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
(matvec products, clipping, etc.), to a Nash
$(\epsilon,0)$-equilibrium of the game.

Equilibrium problems are saddle-point convex-concave problems, and as
such a natural choice for algorithms for solving them would be in the
family of primal-dual algorithms. %%  We believe such primal-dual
%% schemes will receive more attention in the algorithmic game theory
%% community in future.

@@

%\pagebreak
\bibliographystyle{llcns2e/splncs03}
\bibliography{bib}

@@

>>>>

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for
  computing approximate Nash-equilibria in two-person zero-sum
  sequential games with  incomplete information and perfect recall
  (like Texas Hold'em poker). Our algorithm only performs basic
  iterations (i.e matvec multiplications, clipping, etc., and no calls
  to external first-order oracles, no matrix inversions, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with incomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  which allows us to encode any such game
  as a matrix game with convex polytopial profiles. We prove that
  the number of iterations needed to produce a Nash-equilibrium with a
  given precision is inversely proportional to the
  precision. By way of demonstration, we also present experimental
  results on simulated and real games (Kuhn poker).
\end{abstract}

@@

\subsection{Notation and terminology}
Let $m$ and $n$ be positive integers. Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

@@

The interested reader should refer to \cite{combettes2011proximal} and
the references therein, for a more elaborate exposition on
proximal calculus. % and its use in modern convex-optimization.

@@

In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used
to solve the equilibrium problem \eqref{eq:gilpin}.
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop.
\cite{gilpinfirst} proposed a modified version of the techniques in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) \log \left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle. Here
$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
\textit{condition number} for the game. The crux of their technique was to
observe that \eqref{eq:gilpin} can further be written a the minimization of
the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:dgap})
for the game\footnote{The minimizers of $G$ are precisely the
  equilibria of the game.}, viz
\begin{eqnarray}
\mathrm{minimize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
\end{eqnarray}
and then show there exists a scalar
$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
\begin{eqnarray}
\text{``distance between }(x, y)\text{ and the set of
equilibria'' } \le G(x, y)/\delta.
\end{eqnarray}
Their
algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
with a geometrically decreasing sequence of tolerance levels
$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
should be noted however that
\begin{itemize}
\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
\delta\right) \log\left(1 / \epsilon\right)\right)$ convergence rate can
be arbitrarily large for ill-conditioned games.
\item[--] The reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. Most
  notably, the complicated projections $\proj_{Q_k}$ are applied at
  each iteration.%%  Of
  %% course, the existence of a linear algorithm for solving
  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  %% conditions are absent.

@@

\section{Our contributions}
\label{sec:gsp}
\subsection{Preliminaries}
In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
and \eqref{eq:dual_pb} can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}. The crux of idea
is to remove the linear constraints in the definitions of the strategy
polytopes $Q_k$, by modifying the payoff matrix to yield an equivalent
saddle-point problem.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\subsection{Yet another notion of approximate Nash-equilibrium}
\begin{definition}
  Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
  \rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged
  subdifferential (or
  $\epsilon$-subdifferential, for short) of $f$ is the set-valued
  function defined by
  \begin{eqnarray}
\partial_\epsilon f(x):= \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}
\end{definition}
The idea behind $\epsilon$-subdifferentials is the following. Say we wish
to minimize the function $f$. Replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
small vector $v$''. In fact, it is easy to see that, for each
point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.

@@

\subsection{Practical considerations}
\paragraph*{Efficient computation of $Ay$ and $A^Tx$.}
In Algorithms \ref{Tab:algo}, most of the time is spent
pre-multiplying vectors by $A$ and $A^T$ (precisely 3 such operations
are done per iteration). For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagonal structure (each block is itself the
Kronecker product of smaller matrices) which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.%%  For the purpose of
%% completness, we explain the details of the tricks used in
%% \cite{hoda2010smoothing} for speeding up the computation of these
%% matvec products.

@@

\paragraph*{Computing $\|K\|$.}
Also the 2-norm $\|K\|$ of the linear operator $K$, can be efficiently
computed using the power iteration.

\section{Experimental results}
\label{sec:results}
To assess the practical quality of the proposed algorithm, we
tested it on simulated and real games.
\paragraph*{Sequential games with incomplete
  information: Kuhn poker.} This game is a simplified form of poker
developed by Harold W. Kuhn. It is a two-person zero-sum game which is
simple enough to serve as a proof-of-concept example but contains all
the complexity traits of a incomplete information sequential game. The
deck includes only three playing cards: a King, Queen, and
Jack. One card is dealt to each player, then the first player must bet
or pass, then the second player may bet or pass. If any player chooses
to bet the opposing player must bet as well ("call") in order to stay
in the round. After both players pass or bet the player with the
highest card wins the pot.%%  The
%% sequence-form representation of the game has $n_1 = n_2 = 13$
%% sequences and $l_1 = l_2 = 7$ information
%% sets per player. The sequence-form of the game is given by\\\\
%% $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
%% E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
%% E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
%% E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
%% E_1(5,5) = E_1(6,9) = {-1}$; $E_2 \in \mathbb{R}^{7 \times 13}$ with
%% $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
%% E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
%% E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
%% E_2(5,0) = E_2(6,0) = {-1}$; and $A \in \mathbb{R}^{13 \times
%%   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
%% {-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
%% A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
%% A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
%% $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
%% A(12,1) = A(12,5) = {0.166667}$.\\

@@

\begin{figure}[!htpb]
  \subfigure[$10^3 \times 10^3$ matrix game on simplexes]{
    \includegraphics[width=.5\linewidth]{0.pdf}
  }
  %% \hspace{-2em}
  %% \subfigure[Toy poker]{
  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
  %% }
  \hspace{-2em}
  \subfigure[Kuhn 3-card poker]{
    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
  }
  %\vspace{-1em}
  \hspace{-.5em}
  \includegraphics[width=.5\linewidth]{1.pdf}
  %% \hspace{-1em}
  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  %\hspace{.5em}
  \includegraphics[width=.49\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. In \textit{(a)}, the duality gaps
    are computed according to formula \eqref{eq:mg_pd}. One can see
    the linear (i.e exponential) behavior of the algorithm in
    \cite{gilpinfirst}, inbetween consecutive breakpoints on the
    $\epsilon$ grid (though the rate of exponential growth seems to by
    quite close to $1$ here). The first-order smoothing algorithm from
    \cite{nesterov2005a} jitters around as the iterations go on
    because even the smoothed problem becomes heavily ill-conditioned
    near solutions. On the other hand, our proposed
    algorithm beats both of the aforementioned algorithms, and
  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
  verified empirically. \textit{(b)}: Kuhn poker. In both cases we see
  that the proved convergence rate for our algorithm is observed.}
  \label{Tab:dgap_curve}
\end{figure}

\section{Concluding remarks and future work}
Making use of the sequence-form representation
\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
devised a simple and efficient primal-dual algorithm for computing
Nash-equilibria in two-person zero-sum sequential games with
incomplete information (like Texas Hold'em, etc.). Our algorithm is
simple to implement, with a low constant cost per iteration, and
enjoys a rigorous convergence theory with a proven
$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
(matvec products, clipping, etc.), to a Nash
$(\epsilon,0)$-equilibrium of the game.
Equilibrium problems are saddle-point convex-concave problems, and as
such a natural choice for algorithms for solving them would be in the
family of primal-dual algorithms. %%  We believe such primal-dual
%% schemes will receive more attention in the algorithmic game theory
%% community in future.

@@

@@

\pagebreak
\bibliographystyle{IEEEbib}
\bibliography{bib}
